A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-02-24 analysis/paper.Rmd
change fig size

```{r, ori-fig-4, fig.cap="Original figure 4", echo=FALSE}
knitr::include_graphics("figure4-ori.png")
```

```{r, ori-fig-5, fig.cap="Original figure 5", echo=FALSE}
knitr::include_graphics("figure5-ori.png")
```

@@

```{r, rep-fig-4, fig.cap="Replication of figure 4 with new simulation data", echo=FALSE}

@@

```{r, rep-fig-5, fig.cap="Replication of figure 5 with new simulation data", echo=FALSE}

>>>>

```{r, ori-fig-4, fig.cap="Original figure 4", echo=FALSE, out.width="10%"}
knitr::include_graphics("figure4-ori.png")
```

```{r, ori-fig-5, fig.cap="Original figure 5", echo=FALSE, out.width="10%"}
knitr::include_graphics("figure5-ori.png")
```

@@

```{r, rep-fig-4, fig.cap="Replication of figure 4 with new simulation data", echo=FALSE, , fig.width=7, fig.height=4}

@@

```{r, rep-fig-5, fig.cap="Replication of figure 5 with new simulation data", echo=FALSE, , fig.width=7, fig.height=4}
